### 2020-02-25 ChapterBackground/chapterBackground.tex
Updated: Delta-Encoding in Online Gaming

\subsection{Delta-Update}
%TODO: Mention delta-update techniques, advantages and problems created

>>>>

\subsection{Delta-Encoding}
%TODO: Mention Delta-Encoding is used between servers for auras in implementation
A common optimisation used by networked games is delta-encoding. Typically in games entities and their state change little from one update to the next, i.e. it is expected that only a small number of entities change between updates. Delta-encoding reduces network traffic by the server only encoding the difference (delta) between updates, reducing the size of messages that need to be sent \cite{bharambe2006colyseus}. Additionally, if an object's state has not changed, no message is required to be sent, dramatically reducing network overhead in cases of a large number of objects which are not changing. The main drawback of this technique is a missed update message sent to a client would lead to a different entity state from that point for that client and can lead to missing entities or entities that have been deleted on the server, remaining on the client. As result of this, delta-encoding either requires reliable message transmission between server and client or a periodically transmitted full "key" frame, containing the state of all entities \cite{bharambe2004supporting}.
